\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Luca Ghislotti}} & Personal e-mail: \href{mailto:ghislottiluca@gmail.com}{~ghislottiluca@gmail.com}\\
  Website: \href{https://lucaghislotti.com}{~~lucaghislotti.com} & University e-mail: \href{mailto:l.ghislotti@studenti.unibg.it}{~l.ghislotti@studenti.unibg.it}  \\
  Github: \href{https://github.com/lucaghislo}{ ~~github.com/lucaghislo} & Mobile:~~+39 3331133825\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Centro Studi Leonardo da Vinci}{Bergamo, Italy}
      {IT Technical Institute - IT and Telecommunications Course}{September 2012 - June 2017}
    \resumeSubheading
      {Scuola di Ingegneria - Università degli studi di Bergamo}{Dalmine (BG), Italy}
      {Bachelor Degree in Computer Engineering}{September 2017 - September 2020}
    \resumeSubheading
      {Scuola di Ingegneria - Università degli studi di Bergamo}{Dalmine (BG), Italy}
      {Master's Degree in Computer Engineering}{September 2020 - Ongoing}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, PHP, C, C++, C\#, JavaScript, SQL, Bash, Java, LaTeX, Scala, SQL, MIPS Assembly, HTML}
	\resumeSubItem{Frameworks}{~~~~TensorFlow, Keras, NodeJS, Apache Spark, Apache Hadoop}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, MySQL, SQLite, MongoDB, Arduino, Raspberry Pi, XPath, XQuery }
	\resumeSubItem{Platforms}{~~~~~~~Linux, Web, Windows, Arduino, Raspberry, AWS, MacOS, Android, iOS}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management, ECDL (2016)}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------Languages-----------------
\section{Languages}
\begin{description}[font=$\bullet$]
\item {Italian, English (full proficiency), Spanish (A2 level)}
\end{description}
\vspace{-5pt}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Società Agricola le Campagnole}{Cologno al Serio (BG), Italy}
    {(Owner) Organic farm with production and sale of dairy products}{January 2018 - October 2019}
    \resumeSubheading{Efficient Farm Engineering}{Ghisalba (BG), Italy}
    {(Associate) Innovative startup operating in the agricultural sector}{December 2019 - Ongoing}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Where's my car? Sistema di localizzazione GPS}{development project of a GPS tracking device using Arduino, data collection system and web interface. (June '17)}
\vspace{2pt}
\resumeSubItem{Sistema di gestione per rilevatore di velocità con microprocessore MIPS R2000}{development project of a microcontroller programmed in MIPS Assembly for the implementation of a speed detection system. (May '18)}
\vspace{2pt}
\resumeSubItem{Applicazione web BarAPP - Sistema di gestione software per una catena di caffetterie}{development project of a data collection system with a web interface using relational databases. (May '19)}
\vspace{2pt}
\resumeSubItem{Productivity software tool for automated variance and efficiency analysis based on an input dataset}{development project of standalone application for covariance and variance analysis. (Dec '19)}
\vspace{2pt}
\resumeSubItem{MyTEDx Project - Mobile and Cloud Technologies course}{complete server-less project based on AWS Services and Flutter. (Dec '19)}
\vspace{2pt}
\resumeSubItem{Data Anonymization Techniques: Implementation in the Apache Spark Enviroment}{project work regarding the implementation of anonymization techniques using Apache Spark. (Jun '20)}
\vspace{2pt}
\resumeSubItem{Adversarial Machine Learning: problem evaluation and implementation}{computer security course project regarding the analysis of the adversarial machine learning problem using TensorFlow and Keras. (May '21)}
\vspace{2pt}
\resumeSubItem{e-Campus: sistema di gestione mense di un campus universitario}{implementation of the CoCoME case study via REST API using Java and graphical interfaces. (Feb '21)}
\vspace{2pt}
\resumeSubItem{Frame Problem: definizione, casi applicativi e proposte}{research work on the frame problem and the implications this problem has in the context of software design. (Jul '21)}
\vspace{2pt}
\resumeSubItem{Cross-language project work}{programming course project regarding the use of multiple programming languages, namely C and C++, Scala, Java and Python. The project also involves the use of Apache Spark, QT and ASMs. (Sep '21)}
\vspace{2pt}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {“Io e Lode - Studenti Eccellenti Scuole Bergamasche” by Confindustria Bergamo - 2014, 2015, 2016, 2017}
\vspace{-5pt}
\item {Scholarhip - Top Ten Students program by Università degli Studi di Bergamo - 2017, 2020, 2021}
\vspace{-5pt}
\end{description}

\vspace{-5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Contributor at Informatici Senza Frontiere ONLUS}{Milan, Italy}
    {Association created to bridge the digital divide by exploiting information technologies.}{April 2018 - Present}
\vspace{5pt}

\resumeSubHeadingListEnd

\end{document}